The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/olderthan_201909/CIV_notes_20190322.tex
CIV tex/ tidy up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their energy output on timescales of weeks to months. 
This observational fact, and the subsequent mismatch in the expected timescale, the ``viscous'' timescale, 
which for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was noted over 30 years ago \citep[e.g.][]{Alloin1985}. 
However, with new photometric light-curve and repeat spectroscopic data, the desire for a deeper understanding 
of AGN accretion disk physics  has been re-established \citep[e.g.][]{Lawrence2018, Antonucci2018}.

Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs) have now been 
assembled \citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
terms as a cover for the underlying physics. For sake of argument, ``Changing Look'' quasars can be 
thought of as the extension of ``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas 
the ``Changing State'' quasars (CSQs) have a `state-transition' similar to that in Galactic X-ray binaries
\citep[e.g][]{NodaDone2018, Ruan2019}.

While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
%% 
Here, we report on three objects 
SDSS J120544.7+342252.4  (hereafter J1205+3422), 
SDSS J163852.93+282707.7 (hereafter J1638+2827) and
SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in the \civ broad emission line
properties, as well as in the underlying continuum. We claim these are
the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift and for emission lines with high ionization potentials
(I.P.'s $>$13.6 eV).

For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
standard UV/blue continuum slope increases in flux. 
the UV/blue continuum diminishes and the shape of \lya changes.

\subsection{Literature Search}
\citet{Wilhite2006} examine the variability of the high-ionizaton
C~\textsc{iv}$\lambda{1549}$ line in a sample of 105 quasars observed
at multiple epochs by the Sloan Digital Sky Survey.  We find a strong
correlation between the change in the C~\textsc{iv} line flux and the
change in the line width, but no correlations between the change in
flux and changes in line center and skewness.  The relation between
line flux change and line width change is consistent with a model in
which a broad line base varies with greater amplitude than the line
core. The objects studied here are more luminous and at higher
redshift than those normally studied for variability, ranging in
redshift from 1.65 to 4.00 and in absolute $r$-band magnitude from
roughly $-$24 to $-$28.  Using moment analysis line-fitting
techniques, we measure line fluxes, centers, widths and skewnesses for
the C~\textsc{iv} line at two epochs for each object.  The well-known
Baldwin Effect is seen for these objects, with a slope $\beta =
-0.22$.  The sample has a median intrinsic Baldwin Effect slope of
$\beta_{int} = -0.85$; the C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  Additionally, we find
no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
indicating that this blueshift might be useful as a measure of
orientation.

@@

\citet{Grier2015}....
%\includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}

\citep{Corbin1991, Dimitrijevic1992, Wills1993, Brotherton1994, Osmer1994} ...

\citep{Nazarova2003} ...

%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
\subsection{Selection/Identification}

\subsection{SDSS spectra}
\begin{table}
 \centering
 \begin{tabular}{l l l l}
  \hline \hline 
% &&\\
   Quantity \ Object                           & J2228+2201     &  J1638+2827 \\
% &&\\
 \hline 
    &&\\
    R.A. / deg                                        &    337.078194      &  249.720559\\
    Declination / deg                            &    +22.017478      &  +28.452159 \\
    redshift, $z$                                    &   2.222$\pm$0.00038   &  2.185$\pm$0.00043          \\
    &&\\ 
    \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
                                         & 7582, 790, 56960	     & 5201, 178, 55832 \\    
 %   &&\\ 
    %$M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
    %log $(L_{\rm bol} / {\rm erg s}^{-1}) $      &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
    %log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
    %Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
    &&\\
    \hline \hline 
  \end{tabular}
  \caption{Physical properties of J1100-0053, J2317+0005 and J1052+1519 using the
    methods from \citet{Shen2011}. *This spectrum was used to estimate
    the quantities reported.  We use the regular definition of $L_{\rm
      Edd} = 4 \pi G M m_{\rm p} c /\sigma_{T} =
    1.26\times10^{38}\left (M/M_{\odot} \right )$ erg s$^{-1}$.} 
 \label{tab:Shen_props}
\end{table}

Double Spectrograph (DBSP) is a low-to-medium resolution ($R\sim$1,000
to 10,000) grating instrument for the Palomar 200-inch telescope
Cassegrain focus that uses a dichroic (at, e.g., 5200\AA\ ) to split
light into simultaneously observed separate red and blue channels.

The Low Resolution Imaging Spectrometer (LRIS) is a visible-wavelength
imaging and spectroscopy instrument commissioned in 1993 and operating
at the Cassegrain focus of 10-meter Keck I telescope.

\begin{table*}
 \centering
 \begin{tabular}{r  r  r r r   r r r r}
  \hline \hline 
% &&\\
   Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{Mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}   & Exposure    & \multirow{3}{*}{Spectrum} & \multirow{3}{*}{Notes} \\
   R.A. / deg                   &               &               &            &                                &                                                                       &  Time         & & \\
   Decl. / deg                 &               &               &            &                                &                                                                       &  / seconds         & & \\

% &&\\
 \hline 
                                       &                &               &            &                              &                   &                             &  & \\
   J120544.7+342252.4   & 2.071     &   17.99   & 53498 & 2005-May-08   & SDSS             & ?                          & 53498-2089-427  & \\
          181.436164           &                &               & 58538 & 2019-Feb-24     & DBSP            &  2$\times$900    &                               &  Conditions? \\
         +34.381229           &                &               & 58693 & 2019-Jul-29      & DBSP            &  2$\times$1200   &                                &   \\
                                       &                &               &              &                           &                   &                             &  & \\
   J163852.9+282707.7   & 2.182     &   19.77    & 54553 & 2008-Mar-28    & SDSS             & ?                          & 54553-2948-614  & \\
      249.720558407	       &               &              & 55832  & 2011-Sep-28     & BOSS            &   3603                  & 55832-5201-178  & \\
       +28.452158884        &               &              & 58583 & 2019-Apr-10        & LRIS              &  2$\times$900    &   & \\
                                       &                &               &              &                           &                   &                             &  & \\
    J222818.7+220102.9   & 2.222     & 19.97    & 56189 & 2012-Sep-19     & BOSS             &  2702               & 56189-6118-720   & \\
        337.078194              &              &              & 56960 & 2014-Oct-30    & BOSS             & ?                         & 56960-7582-790     & QSO1-REOBS \\ 
        +22.017478                                &               &             & 58693 & 2019-Jul-29      & DBSP              & 2$\times$1200  &       &    \\
                                       &                &               &            &                             &                   &                              &  & \\
%   J232446.7+140029.5   &  0.916     &  18.83   &  56209 & 2012-Oct-09   & BOSS             & ?                             & 56209-6148-743   & \\
 %                                      &                &               &   58662 & 2019-Jun-28  &   (??)DBSP       & ?                            &  & \\
  %                                     &                &               &              &                           &                   &                              &  & \\
   \hline \hline   
  \end{tabular}
  \caption{Spectrum is SDSS/BOSS MJD-Plate-FiberID combination. 
Exposure times are from the {\tt plate.fits} file. 
DBSP on the Palomar 200-inch telescope is the } 
 \label{tab:obs_notes}
\end{table*}

\subsection{J1205+3422 }
SDSS J120544.67+342252.4, observed by SDSS, first reported in \citet{Schneider2007}. 
Redshift of $z=$2.068$\pm$0.00027. 
%% targeting_flags	SERENDIP_BLUE QSO_CAP
plate	2089 
mjd	53498
fiberid	427

\subsection{J1638+2827}
SDSS J163852.93+282707.7       16h38m52.9s +28d27m08s  \\
First reported in \citet{Schneider2010}. 
Selected by {\tt SERENDIP\_BLUE} and {\tt QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
Selected as a $z>2$ known quasar and passed BOSS quasar target selections \citep{Ross2012}.

R.A. (J2000) = 249.72058 degs. \\
Decl. (J2000) = 28.45217 degs. \\
\href{skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232}{SDSS SkyServer} 
All Spectra of this Object:: \\
specObjId	plate	MJD	fiber	ra	dec	redshift \\
5855854441601671168	5201	55832	178	2.186$\pm$0.00073\\
3319321776793610240	2948	54553	614	2.185$\pm$0.00043\\

\subsection{J2228+2201}
SDSS J222818.76+220102.9 (R.A. 337.078194926, Decl. 22.017477924) was first reported in 
\citet{Paris2017}.

%%\href{https://skyserver.sdss.org/dr12/en/tools/chart/navi.aspx?ra=337.077916666667&dec=22.0173888888889&scale=0.2&width=120&height=120&opt=
\href{skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655}{SDSS SkyServer}
All Spectra of this Object:: \\
specObjId	plate	MJD	fiber	ra	dec	redshift \\
8536790363997708288	7582	56960	790	2.222$\pm$0.00038\\
6888453645991387136	6118	56189	720	2.217$\pm$0.00208\\

%Plate: 2948, MJD: 54553, Fiber: 0614
%https://dr12.sdss.org/spectrumDetail?mjd=54553&fiber=614&plateid=2948

\begin{table*}
  \centering
  \begin{tabular}{l  l  l    lll}
    \hline \hline 
    Line 	    &   Rest	      & Line       & Line	       &	Line			                 &   Continuum \\ 
    Name	    &   Wavelength  &  $z$       & $\sigma$ 	&	Flux			                 & \\
                    &    $\AA $        &              & /  km s$-1$	&     10$^{-17}$ erg/cm$2$/s &  10$^{-17}$ erg/cm$^2$/s/\AA  \\
Ly$\alpha$  &	 1215.7	&	2.186      &	1362	&	510.5		                &	7.224 \\
\nv		    &   1240.8	&	2.184     &	 854.6	&	122.4	                    	&	5.546 \\ 
\civ		    &  1549.5	&	2.184    &	1927	&	462.6		                &	2.722 \\ 
\heii	    &	 1640.4	&	2.184    &	1927	&    	  8.067	                   	&	2.447 \\  
\ciii 	    &	 1908.7	&	2.184    &	1927	&	164.6	                   	&	1.966  \\ 
\mgii	    &	 2800.3	&	2.184   & 	1927	&	187.4	                   	&	1.513  \\
   \hline \hline   
  \end{tabular}
  \caption{Line Measurement Information}
 \label{tab:line_values}
\end{table*}

\begin{table*}
  \centering
  \begin{tabular}{l  lll lll  }
    \hline \hline 
                                    &                               &                                           &                                                      &                                  &                         & \\  
                                  \multicolumn{7}{c}{J1638+2827}  \\
                                    &                               &                                           &                                                      &                                  &                         & \\  
   \hline                       
%                                   &                               &                                           &                                                      &                                  &                         & \\  
    Line      	             & Line  $\sigma$     & Line  Flux                           &   Continuum                                 & Line  $\sigma$          & Line  Flux        &   Continuum                                    \\
%    Wavelength	             & /  km s$^{-1}$         &   10$^{-17}$ erg/cm$2$/s  & 10$^{-17}$ erg/cm$^2$/s/\AA      &  /  km s$-1$             & / 10$^{-17}$ erg/cm$2$/s   & /10$^{-17}$ erg/cm$^2$/s/\AA       \\
                                     & \multicolumn{3}{l}{MJD 54553}                                                                                   & \multicolumn{3}{l}{MJD 55832}                                                                                                          \\
    Ly$\alpha$1215.7    &  1362	            &	510.5		                  &	7.224                                           &  1769	                &   633.9	              &  5.376     \\
    \nv1240.8	            &   854.6	            &	122.4	                    	  &	5.546                                           & 1012	                &  107.1		      &  4.645\\ 
    \civ1549.5         	    &	 1927	            &	462.6		                  &	2.722                                           & 2287	                &  125.1		      &  1.256      \\  
    \heii1640.4	            &	 1927    	            &      8.067	                   	  &	2.447                                           & 2287	                &    10.68	      &  1.001\\  
    \ciii1908.7        	    &	 1927	            &	164.6	                   	  &	1.966                                          & 2287	 	                &     29.53	      &  0.6008\\ 
    \mgii2800.3	    &   1927	            &	187.4	                   	  &	1.513                                          & 2287 	 	         &    34.66	      &  0.3461  \\
                                    &                               &                                           &                                                      &                                  &                           &                \\  
   \hline \hline   
  \end{tabular}
  \caption{Line Measurement Information. 
    Line $\sigma$ in units of   km s$-1$; 
    Line flux          in units of  10$^{-17}$ erg/cm$^2$/s; 
    Continuum      in units of  10$^{-17}$ erg/cm$^2$/s/ \AA; 
}
 \label{tab:line_values}
\end{table*}

%Plate: 5201, MJD: 55832, Fiber: 178
%https://dr12.sdss.org/spectrumDetail?mjd=55832&fiber=178&plateid=5201

%Line		Rest		        Line	        Line		        Line			   Continuum
%Name		Wavelength	z	        sigma 		Flux	
%                       [Å]			               [km s-1]  	[10-17erg/cm2/s] 	   [10-17erg/cm2/s/Å]
%Ly_alpha	1215.7		2.186	1769		633.9		   5.376
%N_V		1240.8		2.185	1012		107.1		   4.645
%C_IV		1549.5		2.185	2287		125.1		   1.256
%He_II		1640.4		2.185	2287		 10.68		   1.001
%C_III]		1908.7		2.185	2287	 	 29.53		   0.6008
%Mg_II		2800.3		2.185	2287 	 	 34.66		   0.3461

%So, ratios, MJD 54553 / MJD 55832::
%$Ly_alpha	1215.7		—	0.770		0.805			1.344			
%N_V		1240.8		—	0.844		1.143			1.194
%C_IV		1549.5		—	0.843		3.698			2.167			
%He_II		1640.4		—	0.843		0.755			2.445			
%C_III]		1908.7		—	0.843		5.574			3.27			
%Mg_II		2800.3		—	0.843		5.407			4.37

\subsection{Multi-wavelength properties}
MIR \\
Radio \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{In the context of CLQs at lower-$z$}

\subsection{Balmer CLQs vs. \civ CLQs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}

\bibliographystyle{mnras}
\bibliography{tester_mnras}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
While there have been a slew of studies on carbon IV (\civ) broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}. However, dramatic changes in the 
broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
Here, we report on two objects SDSS J222818.76+220102.9 (hereafter J2228+2201) and 
SDSS J163852.93+282707.7 (hereafter J1638+2827).

For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the
standard UV/blue continnum slope increases in flux. 
For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade, 
the UV/blue continuum diminshes and the shape of \lya changes.

\subsection{Literature Search}

@@

%\includegraphics[]{../../../../../Users/npr1/Downloads/Sun_2015_ApJ_811_42.pdf}

\citet{Grier2015}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Grier_2015_ApJ_806_111.pdf}

%\includegraphics[]{../../../../../Users/npr1/Downloads/mnras0409-0591.pdf}
%%\includegraphics[]{../../../../../Users/npr1/Downloads/Punsly_2010_ApJ_713_232.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/681-689.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1994ApJ___423__131B.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1992A+AS___96__613D.pdf}
%%\includegraphics[]{../../../../../Users/npr1/Downloads/1993IAUS__155___94D.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/1991ApJ___371L__51C.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Joshi_2019_ApJ_871_43.pdf}
%\includegraphics[]{../../../../../Users/npr1/Downloads/Misawa_2007_ApJ_660_152.pdf}
%[]{../../../../../Users/npr1/Downloads/1993ApJ___415__563W.pdf}

\subsection{Carbon IV}
Table~\ref{tab:civ_configs} from 
Atomic Line List version: 2.05b21  
%%Version 2.05b21 of the line list was created: Nov 7, 2017.
\citep{Tunklev1997} \\

\citep[NIST; ][]{Reader2012AAS, Kramida2018}\\

%Wavelength range: 0 - inf   Unit: Angstrom   Type: Vacuum \\
%Radial velocity: 0 km/s\\
%Element/Spectrum: C  IV  \\
%
%-LAB-WAVL-ANG-VAC-|-SPC-|TT|-TERM--|-J\_i-J\_k-|-LVL-EN--CM-1--|-REF---| \\
 % 1548.203         C IV E1  2S-2Po 1/2 - 3/2 0.00 - 64591.00 045 \\
 % 1550.777         C IV E1  2S-2Po 1/2 - 1/2 0.00 - 64483.80 045 \\
%
%  gk*Aki weighted average wavelength:    1549.06    \\
%

\href{https://physics.nist.gov/cgi-bin/ASD/lines1.pl?spectra=C+IV&limits_type=0&low_w=&upp_w=&unit=1&submit=Retrieve+Data&de=0&format=0&line_out=0&en_unit=0&output=0&bibrefs=1&page_size=15&show_obs_wl=1&show_calc_wl=1&unc_out=1&order_out=0&max_low_enrg=&show_av=2&max_upp_enrg=&tsb_value=0&min_str=&A_out=0&intens_out=on&max_str=&allowed_out=1&forbid_out=1&min_accur=&min_intens=&conf_out=on&term_out=on&enrg_out=on&J_out=on}{NIST Atomic Spectra Database Lines Data; C IV: 228 Lines of Data Found}. \\

\href{https://physics.nist.gov/cgi-bin/ASD/energy1.pl?encodedlist=XXT2&de=0&spectrum=C+IV&submit=Retrieve+Data&units=0&format=0&output=0&page_size=15&multiplet_ordered=0&conf_out=on&term_out=on&level_out=on&unc_out=1&j_out=on&lande_out=on&perc_out=on&biblio=on&temp=}{C IV   91 Levels Found
Z = 6, Li isoelectronic sequence}. \\

%%
Kramida, A., Ralchenko, Yu., Reader, J., and NIST ASD Team (2018). NIST Atomic Spectra Database (ver. 5.6.1), [Online]. Available: https://physics.nist.gov/asd [2019, March 22]. National Institute of Standards and Technology, Gaithersburg, MD. DOI: https://doi.org/10.18434/T4W30F

%% 
%% http://www-personal.umich.edu/~cowley/ionen.htm
%% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)

%%\newpage
%%\input{CIV_AtomicLineList_full}
%%\newpage

%%\newpage
%%\input{CIV_AtomicLineList_mid}
%%\newpage

%%\newpage
%%\input{CIV_AtomicLineList}
%\newpage

\begin{table*}
\begin{tabular}{rrr@{ -- }lr@{ -- }lr@{ -- }llrrr@{ -- }rl}
\hline
\multicolumn{1}{c}{$\lambda_{\rm lab}^{\rm obs}$} & \multicolumn{1}{c}{$\Delta\lambda_{\rm lab}^{\rm obs}$} & \multicolumn{2}{c}{Configurations} & \multicolumn{2}{c}{Terms} & $J_i$ & $J_k$ & \multicolumn{1}{c}{$A_{\rm ki}$} & \multicolumn{1}{c}{$\log(gf)$} & TP flags & \multicolumn{2}{c}{Levels}  \\
\multicolumn{1}{c}{\AA } & \multicolumn{1}{c}{\AA} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{1}{c}{s$^{-1}$} & & & \multicolumn{2}{c}{cm$^{-1}$} & \\
\hline
   1548.203  & $2.7-2$ &  $1s^{2}2s$ & $1s^{2}2p$  &       $^{2}{\rm S}$ & $^{2}{\rm P}^\circ$ &  $\frac{1}{2}$ & $\frac{3}{2}$  & $2.65+8$ & $ -0.4198$ &     8 &      $0.00$ &  $64591.00$  \\
   1550.777  & $2.7-2$ &  $1s^{2}2s$ & $1s^{2}2p$  &       $^{2}{\rm S}$ & $^{2}{\rm P}^\circ$ &  $\frac{1}{2}$ & $\frac{1}{2}$  & $2.63+8$ & $ -0.7217$ &     8 &      $0.00$ &  $64483.80$  \\
\hline
\end{tabular}
\label{tab:civ_configs}
\end{table*}

@@

\section{Data}
\begin{table}
 \centering
 \begin{tabular}{l l l l}
  \hline \hline 
% &&\\
   Quantity \ Object                           & J2228+2201     &  J1638+2827 \\
% &&\\
 \hline 
    &&\\
    R.A. / deg                                        &    337.078194      &  249.720559\\
    Declination / deg                            &    +22.017478      &  +28.452159 \\
    redshift, $z$                                    &   2.222$\pm$0.00038   &  2.185$\pm$0.00043          \\
    &&\\ 
    \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
    &                                                   & 7582, 790, 56960	     & 5201, 178, 55832 \\    
    &                                                   &                                         & \\
 %   &&\\ 
    $M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
    log $(L_{\rm bol} / {\rm erg s}^{-1}) $  &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
    log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
    Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
    &&\\
    \hline \hline 
  \end{tabular}
  \caption{Physical properties of J1100-0053, J2317+0005 and J1052+1519 using the
    methods from \citet{Shen2011}. *This spectrum was used to estimate
    the quantities reported.  We use the regular definition of $L_{\rm
      Edd} = 4 \pi G M m_{\rm p} c /\sigma_{T} =
    1.26\times10^{38}\left (M/M_{\odot} \right )$ erg s$^{-1}$.} 
 \label{tab:Shen_props}
\end{table}

\subsection{J2228+2201}
SDSS J222818.76+220102.9 (R.A. 337.078194926, 22.017477924was observed

%%\href{https://skyserver.sdss.org/dr12/en/tools/chart/navi.aspx?ra=337.077916666667&dec=22.0173888888889&scale=0.2&width=120&height=120&opt=
skyserver.sdss.org/dr15/en/tools/explore/summary.aspx?id=1237678579819479655
All Spectra of this Object:: \\
specObjId	plate	MJD	fiber	ra	dec	redshift \\
8536790363997708288	7582	56960	790	2.222$\pm$0.00038\\
6888453645991387136	6118	56189	720	2.217$\pm$0.00208\\

\subsection{J1638+2827}
SDSS J163852.93+282707.7       16h38m52.9s +28d27m08s  \\
Selected by {\tt SERENDIP\_BLUE} and {\it QSO\_MAG\_OUTLIER} in SDSS \citep{Richards2002}, meaning...
Selected as a $z>2$ known quasar and passed BOSS quasar target selections \citep{Ross2012}.

R.A. (J2000) = 249.72058 degs. \\
Decl. (J2000) = 28.45217 degs. \\
skyserver.sdss.org/dr15/en/tools/explore/Summary.aspx?id=1237662301375824232
All Spectra of this Object:: \\
specObjId	plate	MJD	fiber	ra	dec	redshift \\
5855854441601671168	5201	55832	178	2.186$\pm$0.00073\\
3319321776793610240	2948	54553	614	2.185$\pm$0.00043\\

\section{Results}

\section{Discussion and Conclusions}

\bibliographystyle{mnras}
\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}
